### 2015-02-20 fundamentals/impl.tex
list punctuation

In addition to the core functionality of the \Cyclus kernel, which is focused on
the set of capabilities needed to implement an agent-based simulation
with \gls{DRE} a toolkit is provided that assists developers
and users with related simulation and nuclear engineering tasks. The toolkit is
an actively developed part of \Cyclus, with a primarily forward-looking
focus on supporting interesting \textit{in situ} metric analysis tools.

@@

In addition to those that already exist, new tools and computational patterns will
emerge from the archetypes developed within the community of
developers. As these tools gain adoption between projects and demonstrate their
utility to the developer community, they will be considered for screening and
adoption into the kernel as toolkit extensions. Likely extensions include:

\begin{itemize}
\item fuel cycle metrics calculators
\item supportive data tables
\item policy models
\item economic models
\end{itemize}

>>>>

In addition to the core functionality of the \Cyclus kernel, which is focused on
the set of capabilities needed to implement an agent-based simulation
with \gls{DRE}, a toolkit is provided that assists developers
and users with related simulation and nuclear engineering tasks. The toolkit is
an actively developed part of \Cyclus, with a primarily forward-looking
focus on supporting interesting \textit{in situ} metric analysis tools.

@@

In addition to those that already exist, new tools and computational patterns will
emerge from the archetypes developed within the community of
developers. As these tools gain adoption between projects and demonstrate their
utility to the developer community, they will be considered for screening and
adoption into the kernel as toolkit extensions. Likely extensions include

\begin{itemize}
\item fuel cycle metrics calculators,
\item supportive data tables,
\item policy models,
\item and economic models.
\end{itemize}
